SMT-Based Generation of Symbolic Automata \thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2019-03-29 2017-Xudong-SMT/ActaInformatica.tex
Improve the proof of Th.2 after Skype.

The reachability function $computeReachableSubAutomaton$ being called
with the same initial state $\ostate{\tilde{t_0}}$, this state is the
initial state of both $L1_{reach})$ and $L2_{reach})$.

@@

  Suppose that  $\ostate{\tilde{t}}\in States(L2_{reach})$. It is reachable in the result automaton of Algorithm 3, so there exists a sequence of transitions $\ostate{\tilde{t_0}}...\xrightarrow{v_j}...\ostate{\tilde{t}}$ where $Pred_j$ are all satisfiable. Then there exists the same state $\ostate{\tilde{t}}\in States(L1_{reach})$ and $\ostate{\tilde{t_0}}...\xrightarrow{v_i}...\ostate{\tilde{t}}$ where $Pred_i$ are all satisfiable.
From the structure of the algorithms, 
\[\forall \ostate{\tilde{t}}\in States(L2_{reach}), OT = \ostate{\tilde{t}}\xrightarrow{v}\ostate{\tilde{t'}}\in L2_{reach}\]
\[\exists OT' = \ostate{\tilde{t}}\xrightarrow{v'}\ostate{\tilde{t'}}\in L1 \quad s.t.\quad Rename(OT') = OT.\]
where $Pred$ and $Pred'$ are satisfiable.

Then we can get a new longer sequence $\ostate{\tilde{t_0}}...\xrightarrow{v_i}...\ostate{\tilde{t'}}\xrightarrow{v'}\ostate{\tilde{t'}}$ implying that $\ostate{\tilde{t'}}\in States(L1_{reach}),OT'\in L1_{reach}$. So 
$L2_{reach}\subseteq  L1_{reach}$.

%Moreover,
Conversely,
\[\forall OT\notin L2_{reach}, \exists OT'\in L1, Rename(OT') = OT\]
where $Pred$ and $Pred'$ are not satisfiable. Then according to the pruning function in Algorithm 1, $OT'\notin L1_{reach}$. 
As a result, we get that $L1_{reach}=L2_{reach}$, and subsequently, $States(L1_{reach})=States(L2_{reach})$.
%We will construct a mapping $f$: $State(L1-reach)\rightarrow
%State(L2-reach)$.
%\ERIC{I do not understand this, as states are identical. You would
%  rather need mapping betwen transitions ?}
%\begin{enumerate}
%\setlength{\itemindent}{3.5em}
%	\item[(Surjective)] If $\ostate{\tilde{s_0}}=Initial(p)$ then $f(\ostate{\tilde{s}})=\ostate{\tilde{t_0}}=Initial(p)$ must exists, the transitions started from them fulfill that
%	\[\forall \ostate{\tilde{t_0'}}, \ostate{\tilde{t_0}}\xrightarrow{v_j}\ostate{\tilde{t_0'}}\in L_{Smart},\quad \exists\ostate{\tilde{s'}},\ostate{\tilde{s_0}}\xrightarrow{v_i}\ostate{\tilde{s_0'}}\in L.\]
%	The state $\ostate{\tilde{t'}}\in State(L_{Smart})$ and as $Pred_j$ of $\ostate{\tilde{t}}\xrightarrow{v_j}\ostate{\tilde{t_0'}}$ is satisfiable, then if the $Pred_i$ of $\ostate{\tilde{s_0}}\xrightarrow{v_i}\ostate{\tilde{s_0'}}$ is also satisfiable, the state $\ostate{\tilde{s_0'}}$ is reachable in the original open automaton s.t. $\ostate{\tilde{s_0'}}\in State(L1)$, we can construct the mapping
%	\[f(\ostate{\tilde{s_0'}})=\ostate{\tilde{t_0'}}.\]
%	If the $Pred_i$ of $\ostate{\tilde{s_0}}\xrightarrow{v_i}\ostate{\tilde{s_0'}}$ is not satisfiable then two transitions are not matched and $\ostate{\tilde{s_0'}}\notin State(L1)$.
%	
%	Let $\textit{Explored}$, $\textit{Explored}_{Smart}$ respectively mean the explored states set of original algorithm and smart algorithm.
%	
%	Suppose that  $\ostate{\tilde{s}}\in \textit{Explored}$ there is $\ostate{\tilde{t}}\in \textit{Explored}_{Smart}$ where $f(\ostate{\tilde{s}})=\ostate{\tilde{t}}$, there exists a sequence of transitions $\ostate{\tilde{s_0}}...\xrightarrow{v_i}...\ostate{\tilde{s}}$ and $\ostate{\tilde{t_0}}...\xrightarrow{v_j}...\ostate{\tilde{t}}$. 
%	
%	The transitions $\ostate{\tilde{s}}\xrightarrow{v}\ostate{\tilde{s'}}$ and $\ostate{\tilde{t}}\xrightarrow{v}\ostate{\tilde{t'}}$ have several cases:
%	\begin{enumerate}
%		\item[(1)] $\ostate{\tilde{t'}}\in \textit{Explored}_{Smart}$
%		
%		We can find that 
%		 \[\exists\ostate{\tilde{s'}}\in \textit{Explored},\quad \ostate{\tilde{s}}\xrightarrow{v}\ostate{\tilde{s'}}\quad where\quad f(\ostate{\tilde{s'}})=\ostate{\tilde{t'}}.\]
%		\item[(2)] $\ostate{\tilde{t'}}\notin \textit{Explored}_{Smart}$
%		
%		There must has 
%		\[\exists\ostate{\tilde{s'}}\notin \textit{Explored},\quad \ostate{\tilde{s}}\xrightarrow{v'}\ostate{\tilde{s'}}.\]
%		If the $Pred_i$ of $\ostate{\tilde{s}}\xrightarrow{v'}\ostate{\tilde{s'}}$ is satisfiable then there exists a sequence of transitions $\ostate{\tilde{s_0}}...\xrightarrow{v_i}...\ostate{\tilde{s}}\xrightarrow{v'}\ostate{\tilde{s'}}$. So the $\ostate{\tilde{s'}}$ is reachable in the original open automaton, we can construct the mapping
%		\[f(\ostate{\tilde{s'}})=\ostate{\tilde{t'}}.\]
%		If the $Pred_i$ of $\ostate{\tilde{s}}\xrightarrow{v'}\ostate{\tilde{s'}}$ is not satisfiable then two transitions are not matched and $\ostate{\tilde{s'}}\notin State(L1)$.
%	\end{enumerate}	
%	Overall, \[\forall \ostate{\tilde{t}}\in State(L_{Smart}),\quad \exists\ostate{\tilde{s}}\in State(L1), f(\ostate{\tilde{s}})=\ostate{\tilde{t}}.\]
%	\item[(Injective)] If there is a pair of states $\ostate{\tilde{s}} and \ostate{\tilde{t}}$ constructs the mapping $f(\ostate{\tilde{s}})=\ostate{\tilde{t}}$. We can know that $\ostate{\tilde{s}}\in \textit{Explored},\ostate{\tilde{t}}\in \textit{Explored}_{Smart}$.
%	
%	As when there is $\ostate{\tilde{t'}}\in \textit{Explored}_{Smart}$, the state is must be $\ostate{\tilde{s'}}\in \textit{Explored}$ where $f(\ostate{\tilde{s'}})=\ostate{\tilde{t'}}$.
%	So it is a one-to-one mapping.
%\end{enumerate}
%
%Then as the function $f$ is both surjective and injective, it is a bijective function. The theorem is proved.
%
\hfill\qed
\end{proof}

>>>>

The reachability function $computeReachableSubAutomaton$ being called
with the same initial state $\ostate{\tilde{t_0}}$, this state is the
initial state of both $L1_{reach}$ and $L2_{reach}$.

@@

Suppose that  $\ostate{\tilde{t}}\in States(L2_{reach})$. It is reachable in the result automaton of Algorithm 3, so there exists a sequence of transitions 
\[\ostate{\tilde{t_0}}\xrightarrow{l_1}\ostate{\tilde{t_1}}\xrightarrow{l_2}...\xrightarrow{l_{n}}\ostate{\tilde{t}}\] where in each label of the transition $Pred_{l_i}^{i\in [1,n]}$ is satisfiable. For the same state $\ostate{\tilde{t}}\in States(L1_{reach})$, there exists a sequence of transitions \[\ostate{\tilde{t_0}}\xrightarrow{l'_1}\ostate{\tilde{t_1}}\xrightarrow{l'_2}...\xrightarrow{l'_{n}}\ostate{\tilde{t}}\]where for each transition $Rename(\ostate{\tilde{t_{i-1}}}\xrightarrow{l_{i}}\ostate{\tilde{t_{i}}}) = \ostate{\tilde{t_{i-1}}}\xrightarrow{l'_{i}}\ostate{\tilde{t_{i}}}$ and $Pred_{l'_i}^{i\in [1,n]}$ is satisfiable. 
From the structure of the algorithms, 
\[\forall \ostate{\tilde{t}}\in States(L2_{reach}), \ostate{\tilde{t}}\xrightarrow{l'_{n+1}}\ostate{\tilde{t'}}\in L2_{reach}\]
\[\exists \ostate{\tilde{t}}\xrightarrow{l_{n+1}}\ostate{\tilde{t'}}\in L1 \quad s.t.\quad Rename(\ostate{\tilde{t}}\xrightarrow{l_{n+1}}\ostate{\tilde{t'}}) = \ostate{\tilde{t}}\xrightarrow{l'_{n+1}}\ostate{\tilde{t'}})\]
where $Pred_{l_{n+1}}$ and $Pred_{l'_{n+1}}$ are satisfiable.

Then we can get a new longer sequence \[\ostate{\tilde{t_0}}\xrightarrow{l_1}\ostate{\tilde{t_1}}\xrightarrow{l_2}...\xrightarrow{l_{n}}\ostate{\tilde{t}}\xrightarrow{l_{n+1}}\ostate{\tilde{t}}\] \[\Rightarrow\ostate{\tilde{t'}}\in States(L1_{reach})\wedge\ostate{\tilde{t}}\xrightarrow{l_{n+1}}\ostate{\tilde{t'}}\in L1_{reach}\in L1.\] So for arbitrary transition in $L2_{reach}$, there is a same transition in $L1_{reach}$ after renaming its label, then we get
$L2_{reach}\subseteq  L1_{reach}$.

Conversely,
\[\forall \ostate{\tilde{t'}}\notin States(L2_{reach}), \ostate{\tilde{t}}\xrightarrow{l'}\ostate{\tilde{t'}}\notin L2_{reach},\quad\exists \ostate{\tilde{t'}}\in States(L1), \ostate{\tilde{t}}\xrightarrow{l}\ostate{\tilde{t'}}\in L1\]
where $Pred_{l}$ and $Pred_{l'}$ are not satisfiable. As pruning function in Algorithm 1 will remove all the unsatisfiable transitions, then $\ostate{\tilde{t}}\xrightarrow{l}\ostate{\tilde{t'}}\notin L1_{reach}$.

As a result, we get that $L1_{reach}=L2_{reach}$, and subsequently, $States(L1_{reach})=States(L2_{reach})$.
%We will construct a mapping $f$: $State(L1-reach)\rightarrow
%State(L2-reach)$.
%\ERIC{I do not understand this, as states are identical. You would
%  rather need mapping betwen transitions ?}
%\begin{enumerate}
%\setlength{\itemindent}{3.5em}
%	\item[(Surjective)] If $\ostate{\tilde{s_0}}=Initial(p)$ then $f(\ostate{\tilde{s}})=\ostate{\tilde{t_0}}=Initial(p)$ must exists, the transitions started from them fulfill that
%	\[\forall \ostate{\tilde{t_0'}}, \ostate{\tilde{t_0}}\xrightarrow{v_j}\ostate{\tilde{t_0'}}\in L_{Smart},\quad \exists\ostate{\tilde{s'}},\ostate{\tilde{s_0}}\xrightarrow{v_i}\ostate{\tilde{s_0'}}\in L.\]
%	The state $\ostate{\tilde{t'}}\in State(L_{Smart})$ and as $Pred_j$ of $\ostate{\tilde{t}}\xrightarrow{v_j}\ostate{\tilde{t_0'}}$ is satisfiable, then if the $Pred_i$ of $\ostate{\tilde{s_0}}\xrightarrow{v_i}\ostate{\tilde{s_0'}}$ is also satisfiable, the state $\ostate{\tilde{s_0'}}$ is reachable in the original open automaton s.t. $\ostate{\tilde{s_0'}}\in State(L1)$, we can construct the mapping
%	\[f(\ostate{\tilde{s_0'}})=\ostate{\tilde{t_0'}}.\]
%	If the $Pred_i$ of $\ostate{\tilde{s_0}}\xrightarrow{v_i}\ostate{\tilde{s_0'}}$ is not satisfiable then two transitions are not matched and $\ostate{\tilde{s_0'}}\notin State(L1)$.
%	
%	Let $\textit{Explored}$, $\textit{Explored}_{Smart}$ respectively mean the explored states set of original algorithm and smart algorithm.
%	
%	Suppose that  $\ostate{\tilde{s}}\in \textit{Explored}$ there is $\ostate{\tilde{t}}\in \textit{Explored}_{Smart}$ where $f(\ostate{\tilde{s}})=\ostate{\tilde{t}}$, there exists a sequence of transitions $\ostate{\tilde{s_0}}...\xrightarrow{v_i}...\ostate{\tilde{s}}$ and $\ostate{\tilde{t_0}}...\xrightarrow{v_j}...\ostate{\tilde{t}}$. 
%	
%	The transitions $\ostate{\tilde{s}}\xrightarrow{v}\ostate{\tilde{s'}}$ and $\ostate{\tilde{t}}\xrightarrow{v}\ostate{\tilde{t'}}$ have several cases:
%	\begin{enumerate}
%		\item[(1)] $\ostate{\tilde{t'}}\in \textit{Explored}_{Smart}$
%		
%		We can find that 
%		 \[\exists\ostate{\tilde{s'}}\in \textit{Explored},\quad \ostate{\tilde{s}}\xrightarrow{v}\ostate{\tilde{s'}}\quad where\quad f(\ostate{\tilde{s'}})=\ostate{\tilde{t'}}.\]
%		\item[(2)] $\ostate{\tilde{t'}}\notin \textit{Explored}_{Smart}$
%		
%		There must has 
%		\[\exists\ostate{\tilde{s'}}\notin \textit{Explored},\quad \ostate{\tilde{s}}\xrightarrow{v'}\ostate{\tilde{s'}}.\]
%		If the $Pred_i$ of $\ostate{\tilde{s}}\xrightarrow{v'}\ostate{\tilde{s'}}$ is satisfiable then there exists a sequence of transitions $\ostate{\tilde{s_0}}...\xrightarrow{v_i}...\ostate{\tilde{s}}\xrightarrow{v'}\ostate{\tilde{s'}}$. So the $\ostate{\tilde{s'}}$ is reachable in the original open automaton, we can construct the mapping
%		\[f(\ostate{\tilde{s'}})=\ostate{\tilde{t'}}.\]
%		If the $Pred_i$ of $\ostate{\tilde{s}}\xrightarrow{v'}\ostate{\tilde{s'}}$ is not satisfiable then two transitions are not matched and $\ostate{\tilde{s'}}\notin State(L1)$.
%	\end{enumerate}	
%	Overall, \[\forall \ostate{\tilde{t}}\in State(L_{Smart}),\quad \exists\ostate{\tilde{s}}\in State(L1), f(\ostate{\tilde{s}})=\ostate{\tilde{t}}.\]
%	\item[(Injective)] If there is a pair of states $\ostate{\tilde{s}} and \ostate{\tilde{t}}$ constructs the mapping $f(\ostate{\tilde{s}})=\ostate{\tilde{t}}$. We can know that $\ostate{\tilde{s}}\in \textit{Explored},\ostate{\tilde{t}}\in \textit{Explored}_{Smart}$.
%	
%	As when there is $\ostate{\tilde{t'}}\in \textit{Explored}_{Smart}$, the state is must be $\ostate{\tilde{s'}}\in \textit{Explored}$ where $f(\ostate{\tilde{s'}})=\ostate{\tilde{t'}}$.
%	So it is a one-to-one mapping.
%\end{enumerate}
%
%Then as the function $f$ is both surjective and injective, it is a bijective function. The theorem is proved.
%
\hfill\qed
\end{proof}
